---
title: "R Notebook"
output: html_notebook
---

#Exploring GBS quality

## Missingness per individual

```{r}

imiss <- read.delim(file = "/run/user/1000/gvfs/sftp:host=cbsugore02.tc.cornell.edu/workdir/rjl278/Sorghum/GBS/GBS_matching.imiss", header = T)
imiss
hist(imiss$F_MISS, main =  "Distribution of missingness per individual")

```

## Missingness per site basis 

```{r}

lmiss <- read.delim(file = "/run/user/1000/gvfs/sftp:host=cbsugore02.tc.cornell.edu/workdir/rjl278/Sorghum/GBS/GBS_matching.lmiss", header = T)
lmiss
hist(lmiss$F_MISS, main =  "Distribution of missingness per site")

```

## SNP density in the GBS dataset before imputation

```{r, fig.width= 15, fig.height=5}

snpden <- read.delim(file = "/run/user/1000/gvfs/sftp:host=cbsugore02.tc.cornell.edu/workdir/rjl278/Sorghum/GBS/GBS_matching.snpden.toplot", header = T)
colnames(snpden) <- c("SNP","CHR", "BP", "n")
snpden$CHR <- as.integer(as.numeric(as.character(snpden$CHR)))
snpden

library(qqman)
library(wesanderson)
wes <- wes_palette("Chevalier")



manhattan(snpden, cex = 0.5, p = "n", logp = FALSE, ylab = "SNPs/kb", genomewideline = FALSE, col = wes,
    suggestiveline = FALSE, main = "GBS density", ylim = (c(0,1.1)) )


manhattan(subset(snpden, CHR ==5, cex = 0.5), p = "n", logp = FALSE, ylab = "SNPs/kb", genomewideline = FALSE, col = wes,
    suggestiveline = FALSE, main = "GBS density", ylim = (c(0,1)) )
 

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
