---
title: "R Notebook"
output: html_notebook
---

Re-running burden calculations

```{r}

library(dplyr)
library(magrittr)
library(tidyr)
library(tidyverse)
library(ggplot2)
library(patchwork)
library(wesanderson)
library(GDAtools)


daf <- read.delim( file = "/workdir/rjl278/Sorghum/Evol_model/Derived_alleles/splitting/FULL_norep.DAF", header =  T) %>%
  mutate(Class = case_when(DAF_p >= 0.55 & Ref_count > Alt_count ~ "Ancestral",
                          DAF_p >= 0.55 & Alt_count > Ref_count ~ "Derived",
                          DAF_p <=0.45 & Ref_count > Alt_count ~ "Derived",
                          DAF_p <=0.45 & Alt_count > Ref_count ~ "Ancestral",
                          DAF_p <0.55 & DAF_p > 0.45 ~ "NA") ) %>%
  mutate(DAF = case_when(Class == "Ancestral" ~ Alt_count/(Ref_count + Alt_count),
                         Class == "Derived" ~ Ref_count/(Ref_count + Alt_count))) %>%
  dplyr::select(-maize1_v4, -maize2_v4, -viridis, -SIFT, -SIFT_score, -Type, -MAF, -maize1_v3, -maize2_v3, -DAF_p ) %>%
  filter(Class == "Ancestral") %>%
  mutate(SETO = case_when(GERP > 0 ~ "Deleterious",
                          GERP <=0 ~ "NonDeleterious")) %>%
  mutate(Bin = cut(DAF, breaks=seq(0, 1, 0.01), labels=seq(0, 0.99, 0.01))) %>%
  mutate(gerp_round = round(GERP))

t <- plyr::count(daf, c('Bin', 'gerp_round'))
t_wide <- spread(t, gerp_round, freq)
t_wide_prop <- cbind(t_wide[1], prop.table(as.matrix(t_wide[-1]), margin=1))

tdel <- plyr::count(daf, c('Bin', 'SETO'))
tdel_wide <- spread(tdel, SETO, freq)
tdel_wide_prop <- cbind(tdel_wide[1], prop.table(as.matrix(tdel_wide[-1]), margin=1))

bias <- tdel_wide_prop %>%
  left_join(t_wide_prop, by="Bin") %>%
  select(Bin, Deleterious, NonDeleterious, "2")

##################################################################

daf_all <- read.delim( file = "/workdir/rjl278/Sorghum/Evol_model/Derived_alleles/splitting/FULL_norep.DAF", header =  T) %>%
  mutate(Class = case_when(DAF_p >= 0.55 & Ref_count > Alt_count ~ "Ancestral",
                          DAF_p >= 0.55 & Alt_count > Ref_count ~ "Derived",
                          DAF_p <=0.45 & Ref_count > Alt_count ~ "Derived",
                          DAF_p <=0.45 & Alt_count > Ref_count ~ "Ancestral",
                          DAF_p <0.55 & DAF_p > 0.45 ~ "NA") ) %>%
  mutate(DAF = case_when(Class == "Ancestral" ~ Alt_count/(Ref_count + Alt_count),
                         Class == "Derived" ~ Ref_count/(Ref_count + Alt_count))) %>%
  select(-maize1_v4, -maize2_v4, -viridis, -SIFT, -SIFT_score, -Type, -MAF, -maize1_v3, -maize2_v3, -DAF_p ) %>%
  mutate(Bin = cut(DAF, breaks=seq(0, 1, 0.01), labels=seq(0, 0.99, 0.01))) %>%
  mutate(gerp_round = round(GERP)) %>%
  mutate(SETO = case_when(GERP >= 2 ~ "Deleterious",
                          GERP <2 ~ "NonDeleterious"))

daf_bias <- daf_all %>%
  left_join(bias, by="Bin") %>%
  mutate(tmp = case_when(   Class == "Ancestral" ~ 1,
                            SETO == "Deleterious" ~ Deleterious,
                            SETO == "NonDeleterious" ~ NonDeleterious)) %>%
  mutate(weight = case_when(is.na(tmp) ~ 1,
                            !is.na(tmp) ~ tmp )) %>%
  dplyr::select(DAF, SETO, weight, GERP) %>%
  na.omit(DAF)

```


## DAF, only GERP > 2

```{r}

#######  Deleterious.-

del <- daf_bias
del$bins <- cut(del$DAF, breaks=c(0,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,1), 
                labels=c("1","2","3", "4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20")) 
del <- del %>%
  filter(GERP >= 2)

de2m            <- as.data.frame(matrix(nrow = 20, ncol = 3,0))
colnames(de2m)  <- c("SET", "Proportion", "DAF_group")
de2m$SET        <- "Deleterious"
de2m$Proportion <- prop.table(wtable(del$bins, w = del$weight)[1:20,1])
de2m$DAF_group  <- c("1","2","3", "4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20")

#######  Synonymous.-

syn <- daf_bias
syn$bins <- cut(syn$DAF, breaks=c(0,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,1), 
                labels=c("1","2","3", "4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20")) 
syn <- syn %>%
  filter(GERP < 2)

syn2m            <- as.data.frame(matrix(nrow = 20, ncol = 3,0))
colnames(syn2m)  <- c("SET", "Proportion", "DAF_group")
syn2m$SET        <- "Synonymous"
syn2m$Proportion <- prop.table(wtable(syn$bins, w = syn$weight)[1:20,1])
syn2m$DAF_group  <- c("1","2","3", "4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20")

###########################################################

## MERGE THE DATA:

merged <- rbind(de2m, syn2m)
merged <- merged%>%
  mutate(YYY = case_when (DAF_group == "1" ~ "0.00-0.05",
                          DAF_group == "2" ~ "0.05-0.10",
                          DAF_group == "3" ~ "0.10-0.15",
                          DAF_group == "4" ~ "0.15-0.20",
                          DAF_group == "5" ~ "0.20-0.25",
                          DAF_group == "6" ~ "0.25-0.30",
                          DAF_group == "7" ~ "0.30-0.35",
                          DAF_group == "8" ~ "0.35-0.40",
                          DAF_group == "9" ~ "0.40-0.45",
                          DAF_group == "10" ~ "0.45-0.50",
                          DAF_group == "11" ~ "0.50-0.55",
                          DAF_group == "12" ~ "0.55-0.60",
                          DAF_group == "13" ~ "0.60-0.65",
                          DAF_group == "14" ~ "0.65-0.70",
                          DAF_group == "15" ~ "0.70-0.75",
                          DAF_group == "16" ~ "0.75-0.80",
                          DAF_group == "17" ~ "0.80-0.85",
                          DAF_group == "18" ~ "0.85-0.90",
                          DAF_group == "19" ~ "0.90-0.95",
                          DAF_group == "20" ~ "0.95-1.00") )



merged$DAF_group <- as.factor(merged$DAF_group)
levels(merged$DAF_group)
merged$DAF_group <- factor(merged$DAF_group, levels = c("1","2","3", "4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20"))

## PLOT

library(wesanderson)
library(ggplot2)
wes =wes_palette("Cavalcanti1")
weso = c(wes[1],wes[2],wes[5],wes[3],wes[4])

newmerge <- merged
newmerge$SET <- as.character(newmerge$SET) 
newmerge <- newmerge %>%
  mutate(SET =replace(SET, SET=="Deleterious", "Deleterious (GERP => 2)")) %>%
  mutate(SET =replace(SET, SET=="Synonymous", "Non-deleterious (GERP < 2)"))

Graph <- ggplot(data=newmerge, aes(x=YYY, y=Proportion, fill=SET)) +
  geom_bar(stat="identity", position=position_dodge())+
  ylab("Proportion of SNPs") +
  xlab("Derived allele frequencies (DAF)") +
  scale_fill_manual(values=weso)+
  theme_minimal() +
  theme(axis.text.x = element_text(face="bold", size=9, angle=90)) +
  guides(fill=guide_legend(title="")) +
  ylim(0, 0.8)

Graph 

```

## DAF, only GERP > 0

```{r}

#######  Deleterious.-

del <- daf_bias
del$bins <- cut(del$DAF, breaks=c(0,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,1), 
                labels=c("1","2","3", "4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20")) 
del <- del %>%
  filter(GERP > 0)

de2m            <- as.data.frame(matrix(nrow = 20, ncol = 3,0))
colnames(de2m)  <- c("SET", "Proportion", "DAF_group")
de2m$SET        <- "Deleterious"
de2m$Proportion <- prop.table(wtable(del$bins, w = del$weight)[1:20,1])
de2m$DAF_group  <- c("1","2","3", "4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20")

#######  Synonymous.-

syn <- daf_bias
syn$bins <- cut(syn$DAF, breaks=c(0,0.05,0.1,0.15,0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85,0.9,0.95,1), 
                labels=c("1","2","3", "4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20")) 
syn <- syn %>%
  filter(GERP <= 0)

syn2m            <- as.data.frame(matrix(nrow = 20, ncol = 3,0))
colnames(syn2m)  <- c("SET", "Proportion", "DAF_group")
syn2m$SET        <- "Synonymous"
syn2m$Proportion <- prop.table(wtable(syn$bins, w = syn$weight)[1:20,1])
syn2m$DAF_group  <- c("1","2","3", "4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20")

###########################################################

## MERGE THE DATA:

merged <- rbind(de2m, syn2m)
merged <- merged%>%
  mutate(YYY = case_when (DAF_group == "1" ~ "0.00-0.05",
                          DAF_group == "2" ~ "0.05-0.10",
                          DAF_group == "3" ~ "0.10-0.15",
                          DAF_group == "4" ~ "0.15-0.20",
                          DAF_group == "5" ~ "0.20-0.25",
                          DAF_group == "6" ~ "0.25-0.30",
                          DAF_group == "7" ~ "0.30-0.35",
                          DAF_group == "8" ~ "0.35-0.40",
                          DAF_group == "9" ~ "0.40-0.45",
                          DAF_group == "10" ~ "0.45-0.50",
                          DAF_group == "11" ~ "0.50-0.55",
                          DAF_group == "12" ~ "0.55-0.60",
                          DAF_group == "13" ~ "0.60-0.65",
                          DAF_group == "14" ~ "0.65-0.70",
                          DAF_group == "15" ~ "0.70-0.75",
                          DAF_group == "16" ~ "0.75-0.80",
                          DAF_group == "17" ~ "0.80-0.85",
                          DAF_group == "18" ~ "0.85-0.90",
                          DAF_group == "19" ~ "0.90-0.95",
                          DAF_group == "20" ~ "0.95-1.00") )



merged$DAF_group <- as.factor(merged$DAF_group)
levels(merged$DAF_group)
merged$DAF_group <- factor(merged$DAF_group, levels = c("1","2","3", "4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20"))

## PLOT

library(wesanderson)
library(ggplot2)
wes =wes_palette("Cavalcanti1")
weso = c(wes[1],wes[2],wes[5],wes[3],wes[4])

newmerge <- merged
newmerge$SET <- as.character(newmerge$SET) 
newmerge <- newmerge %>%
  mutate(SET =replace(SET, SET=="Deleterious", "Deleterious (GERP > 0)")) %>%
  mutate(SET =replace(SET, SET=="Synonymous", "Non-deleterious (GERP <= 0)"))

Graph <- ggplot(data=newmerge, aes(x=YYY, y=Proportion, fill=SET)) +
  geom_bar(stat="identity", position=position_dodge())+
  ylab("Proportion of SNPs") +
  xlab("Derived allele frequencies (DAF)") +
  scale_fill_manual(values=weso)+
  theme_minimal() +
  theme(axis.text.x = element_text(face="bold", size=9, angle=90)) +
  guides(fill=guide_legend(title="")) +
  ylim(0,0.8)

Graph 


```

## Merging del info with dosage file 

```{r}

deleterious <- read.delim( file = "/workdir/rjl278/Sorghum/Evol_model/Derived_alleles/splitting/FULL.DAF", header =  T) %>%
  mutate(Class = case_when(DAF_p >= 0.65 & Ref_count > Alt_count ~ "Ancestral",
                          DAF_p >= 0.65 & Alt_count > Ref_count ~ "Derived",
                          DAF_p <=0.35 & Ref_count > Alt_count ~ "Derived",
                          DAF_p <=0.35 & Alt_count > Ref_count ~ "Ancestral",
                          DAF_p <0.65 & DAF_p > 0.35 ~ "NA") ) %>%
  mutate(DAF = case_when(Class == "Ancestral" ~ MAF,
                         Class == "Derived" ~ 1-MAF) ) %>%
  filter(GERP > 0) %>%
  select(Chr, Position, SET, Class, MAF) %>%
  na.omit(Class)

del <- deleterious %>%
  filter(Class != "NA")

write.table(x = del, file = "/workdir/rjl278/Sorghum/Evol_model/Burden/burden_manuscript_gerp0_.table", sep = "\t", row.names = FALSE, quote = F )




info <- read.delim("/workdir/rjl278/Sorghum/Evol_model/Burden/burden_manuscript_gerp0_ready.table") %>%
  select(CHR_POS, SET, Class, MAF)

markers <- read.delim("/workdir/rjl278/Sorghum/Evol_model/Burden/Dosage.superready") %>%
  select(CHR_POS, COUNTED, ALT) %>%
  inner_join(info, by="CHR_POS")

header <- read.delim("/workdir/rjl278/Sorghum/Evol_model/Burden/header", header = F) 

matriz <- read.delim("/workdir/rjl278/Sorghum/Evol_model/Burden/Dosage.superready") %>%
  select(-COUNTED, -ALT) %>%
  `colnames<-`(header[,1])
  
Master <- markers %>%
  inner_join(matriz, by="CHR_POS")


```

```{r}
# ADD the Weights
daf_all <- read.delim( file = "/workdir/rjl278/Sorghum/Evol_model/Derived_alleles/splitting/FULL.DAF", header =  T) %>%
  mutate(Class = case_when(DAF_p >= 0.55 & Ref_count > Alt_count ~ "Ancestral",
                          DAF_p >= 0.55 & Alt_count > Ref_count ~ "Derived",
                          DAF_p <=0.45 & Ref_count > Alt_count ~ "Derived",
                          DAF_p <=0.45 & Alt_count > Ref_count ~ "Ancestral",
                          DAF_p <0.55 & DAF_p > 0.45 ~ "NA") ) %>%
  mutate(DAF = case_when(Class == "Ancestral" ~ Alt_count/(Ref_count + Alt_count),
                         Class == "Derived" ~ Ref_count/(Ref_count + Alt_count))) %>%
  select(-maize1_v4, -maize2_v4, -viridis, -SIFT, -SIFT_score, -Type, -MAF, -maize1_v3, -maize2_v3, -DAF_p ) %>%
  mutate(Bin = cut(DAF, breaks=seq(0, 1, 0.01), labels=seq(0, 0.99, 0.01))) %>%
  mutate(gerp_round = round(GERP)) %>%
  mutate(SETO = case_when(GERP > 0 ~ "Deleterious",
                          GERP <= 0 ~ "NonDeleterious"))

daf_bias <- daf_all %>%
  left_join(bias, by="Bin") %>%
  mutate(tmp = case_when(   Class == "Ancestral" ~ 1,
                            SETO == "Deleterious" ~ Deleterious,
                            SETO == "NonDeleterious" ~ NonDeleterious)) %>%
  mutate(weight = case_when(is.na(tmp) ~ 1,
                            !is.na(tmp) ~ tmp )) %>%
  mutate(CHR_POS = case_when(  Chr == "Chr01" ~ paste("1_", Position, sep = ""),
                            Chr == "Chr02" ~ paste("2_", Position, sep = ""),
                            Chr == "Chr03" ~ paste("3_", Position, sep = ""),
                            Chr == "Chr04" ~ paste("4_", Position, sep = ""),
                            Chr == "Chr05" ~ paste("5_", Position, sep = ""),
                            Chr == "Chr06" ~ paste("6_", Position, sep = ""),
                            Chr == "Chr07" ~ paste("7_", Position, sep = ""),
                            Chr == "Chr08" ~ paste("8_", Position, sep = ""),
                            Chr == "Chr09" ~ paste("9_", Position, sep = ""),
                            Chr == "Chr10" ~ paste("10_", Position, sep = ""))) %>%
  dplyr::select(CHR_POS, weight) %>%
  na.omit(DAF)


Master <- Master %>%
  left_join(daf_bias, by = "CHR_POS")

derivao <- Master %>%
  filter(Class == "Derived")

for (i in 7:491){
  derivao[,i][derivao[,i] == 0] <- "ZERO"
  derivao[,i][derivao[,i] == 2] <- "TWO"
}

for (i in 7:491){
  derivao[,i][derivao[,i] == "ZERO"] <- as.numeric(2)
  derivao[,i][derivao[,i] == "TWO"] <- as.numeric(0)
  derivao[,i] <- as.numeric(derivao[,i])
}
  


##
ancestral <- Master %>%
  filter(Class == "Ancestral") 


Ready <- rbind(ancestral, derivao)

```

```{r}

#Calculating different burden levels
library(ggplot2)

header <- read.delim("/workdir/rjl278/Sorghum/Evol_model/Burden/header") 

burden_table <- as.data.frame(matrix(nrow= 485,ncol=2))
burden_table[,1] <- header
colnames(burden_table) <- c("ID", "Burden")


valores <- vector()
for (i in 7:491){
  name <- colnames(Ready)[i]
  tabla <- table(Ready[,i])
  a <- Ready %>%
    select(i, weight) %>%
    filter(get(name) == 2)
  load <-  sum(a$weight)/sum(tabla)
  counts <- sum(a$weight)
  valores <- c(valores, load)
}


burden_table$Burden <- valores

race <- read.delim("/workdir/rjl278/Sorghum/Evol_model/Burden/race", header = F) %>%
  `colnames<-`(c("ID", "Race"))

only_race <- race %>%
  inner_join(burden_table, by="ID")


pal <- wes_palette("FantasticFox1", 8, type = "continuous")
wes <- wes_palette("Cavalcanti1")
chev <- wes_palette("Chevalier1")
fox <- wes_palette("FantasticFox1")

colors <- c( fox[1], fox[3], "grey", wes[1], chev[1],"red", "gray31", fox[5])
colors <- c( "darkblue", "grey", "grey", "grey", "grey", "grey", fox[5], fox[5])

p1<-ggplot(only_race, aes(x=Race, y=Burden, fill=Race)) +
  geom_boxplot() +
  scale_fill_manual(values = colors)+
  theme(axis.line = element_line(size=1, colour = "black"),
        panel.grid.major = element_line(colour = "#d3d3d3"), panel.grid.minor = element_blank(),
        panel.border = element_blank(), panel.background = element_blank()) +
  #scale_y_continuous(labels = dollar_format(suffix = "%", prefix = "")) +
  theme(plot.title = element_text(size = 14, face = "bold"),
        axis.text.x=element_text(colour="black", size = 10),
        axis.text.y=element_text(colour="black", size = 10),
        legend.key = element_rect(fill = "transparent", colour = "transparent")) +
  theme(legend.position="none", legend.direction="vertical",
        legend.title = element_blank())# +
  #ylim(0,0.125)

p1


```

```{r}
#Calculating different burden levels
library(ggplot2)

header <- read.delim("/workdir/rjl278/Sorghum/Evol_model/Burden/header") 

burden_table <- as.data.frame(matrix(nrow= 485,ncol=2))
burden_table[,1] <- header
colnames(burden_table) <- c("ID", "Burden")


valores <- vector()
for (i in 7:491){
  name <- colnames(Ready)[i]
  tabla <- table(Ready[,i])
  a <- Ready %>%
    select(i, weight) %>%
    filter(get(name) == 2)
  load <-  sum(a$weight)/sum(tabla)
  counts <- sum(a$weight)
  valores <- c(valores, load)
}


burden_table$Burden <- valores

race <- read.delim("/workdir/rjl278/Sorghum/Evol_model/Burden/race", header = F) %>%
  `colnames<-`(c("ID", "Race"))

only_race <- race %>%
  inner_join(burden_table, by="ID")


pal <- wes_palette("FantasticFox1", 8, type = "continuous")
wes <- wes_palette("Cavalcanti1")
chev <- wes_palette("Chevalier1")
fox <- wes_palette("FantasticFox1")

colors <- c( fox[1], fox[3], "grey", wes[1], chev[1],"red", "gray31", fox[5])
colors <- c( "darkblue", "grey", "grey", "grey", "grey", "grey", fox[5], fox[5])

p1<-ggplot(only_race, aes(x=Race, y=Burden, fill=Race)) +
  geom_boxplot() +
  scale_fill_manual(values = colors)+
  theme(axis.line = element_line(size=1, colour = "black"),
        panel.grid.major = element_line(colour = "#d3d3d3"), panel.grid.minor = element_blank(),
        panel.border = element_blank(), panel.background = element_blank()) +
  #scale_y_continuous(labels = dollar_format(suffix = "%", prefix = "")) +
  theme(plot.title = element_text(size = 14, face = "bold"),
        axis.text.x=element_text(colour="black", size = 10),
        axis.text.y=element_text(colour="black", size = 10),
        legend.key = element_rect(fill = "transparent", colour = "transparent")) +
  theme(legend.position="none", legend.direction="vertical",
        legend.title = element_blank())# +
  #ylim(0,0.125)

p1


```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
