---
title: "GERP histograms"
output: html_notebook
---

# GERP Histogram considering all positions 

```{r}

chromosome1  <- read.delim("/home/roberto/Sorghum/Evol_model/Elodie/tau_SIFT_GERP_infiles/GERP_scores/input_data/roast.chrom.1.msa.in.rates.full", header = F)
chromosome2  <- read.delim("/home/roberto/Sorghum/Evol_model/Elodie/tau_SIFT_GERP_infiles/GERP_scores/input_data/roast.chrom.2.msa.in.rates.full", header = F)
chromosome3  <- read.delim("/home/roberto/Sorghum/Evol_model/Elodie/tau_SIFT_GERP_infiles/GERP_scores/input_data/roast.chrom.3.msa.in.rates.full", header = F)
chromosome4  <- read.delim("/home/roberto/Sorghum/Evol_model/Elodie/tau_SIFT_GERP_infiles/GERP_scores/input_data/roast.chrom.4.msa.in.rates.full", header = F)
chromosome5  <- read.delim("/home/roberto/Sorghum/Evol_model/Elodie/tau_SIFT_GERP_infiles/GERP_scores/input_data/roast.chrom.5.msa.in.rates.full", header = F)
chromosome6  <- read.delim("/home/roberto/Sorghum/Evol_model/Elodie/tau_SIFT_GERP_infiles/GERP_scores/input_data/roast.chrom.6.msa.in.rates.full", header = F)
chromosome7  <- read.delim("/home/roberto/Sorghum/Evol_model/Elodie/tau_SIFT_GERP_infiles/GERP_scores/input_data/roast.chrom.7.msa.in.rates.full", header = F)
chromosome8  <- read.delim("/home/roberto/Sorghum/Evol_model/Elodie/tau_SIFT_GERP_infiles/GERP_scores/input_data/roast.chrom.8.msa.in.rates.full", header = F)
chromosome9  <- read.delim("/home/roberto/Sorghum/Evol_model/Elodie/tau_SIFT_GERP_infiles/GERP_scores/input_data/roast.chrom.9.msa.in.rates.full", header = F)
chromosome10 <- read.delim("/home/roberto/Sorghum/Evol_model/Elodie/tau_SIFT_GERP_infiles/GERP_scores/input_data/roast.chrom.10.msa.in.rates.full", header = F)

new <- rbind(chromosome1, chromosome2, chromosome3, chromosome4, chromosome5, chromosome6, chromosome7, chromosome8, chromosome9, chromosome10)

rm(chromosome1)
rm(chromosome2)
rm(chromosome3)
rm(chromosome4)
rm(chromosome5)
rm(chromosome6)
rm(chromosome7)
rm(chromosome8)
rm(chromosome9)
rm(chromosome10)

hist(new$V2, ylab = "number of sites", xlab = "GERP scores", main = "GERP score distribution")

```

# GERP Histogram considering only positions inside CDS 

```{r}

GERP_CDS  <- read.delim("/home/roberto/Sorghum/Evol_model/Elodie/tau_SIFT_GERP_infiles/GERP_scores/input_data/GERP_CDS.short", header = F)
hist(GERP_CDS$V2, ylab = "number of sites", xlab = "GERP scores", main = "GERP score distribution inside CDS")

```


# How many nucleotides are constrained?

```{r}

constrained <- new %>%
  filter(V2 > 0)

CDSconstrained <- GERP_CDS %>%
  filter(V2 > 0)
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
