---
title: "MAF per population"
output: html_notebook
---

# Allele frequency spectrum 

```{r}


library(ggplot2)
library(ggridges)

caudatum <- read.delim("/home/roberto/Sorghum/Evol_model/LD/MAF/caudatum.hist", header = F) %>%
  `colnames<-`(c("val")) %>%
  mutate(Race="caudatum")
durra <- read.delim("/home/roberto/Sorghum/Evol_model/LD/MAF/durra.hist", header = F) %>%
 `colnames<-`(c("val")) %>%
  mutate(Race="durra")
kafir <- read.delim("/home/roberto/Sorghum/Evol_model/LD/MAF/kafir.hist", header = F) %>%
 `colnames<-`(c("val")) %>%
  mutate(Race="kafir")
guinea <- read.delim("/home/roberto/Sorghum/Evol_model/LD/MAF/guinea.hist", header = F) %>%
   `colnames<-`(c("val")) %>%
  mutate(Race="guinea")

ready <- rbind(caudatum, durra, kafir, guinea)



ridge <- ggplot(ready, aes(x = val, y = Race, fill=Race)) + geom_density_ridges() +
  theme_ridges(grid = FALSE, center_axis_labels = TRUE) +
  xlab("Reference allele frequency") +
  ylab("")

ggsave("/home/roberto/Sorghum/Figures/FigS6B", plot= ridge, device = "png", scale = 1, width = 6, height = 3, units = c("in"),dpi = 200, limitsize = TRUE)

```


# FST

```{r}

library(gdsfmt)
library(SNPRelate)
library(dplyr)
library(magrittr)
library(tidyr)

# Get the path of the plink files
bed.fn <- "/home/roberto/Sorghum/WGS/VCF_2.0/PCA/TERRA_remover.bed"
fam.fn <- "/home/roberto/Sorghum/WGS/VCF_2.0/PCA/TERRA_remover.fam"
bim.fn <- "/home/roberto/Sorghum/WGS/VCF_2.0/PCA/TERRA_remover.bim"

# Build the gdsdb
snpgdsBED2GDS(bed.fn, fam.fn, bim.fn,out.gdsfn ="fst.gds")
snpgdsSummary("fst2.gds")
genofile <- snpgdsOpen("fst.gds")


caudatum <- read.delim("/home/roberto/Sorghum/Evol_model/LD/MAF/caudatum", header = F) %>%
  `colnames<-`(c("ID", "tmp")) %>%
  mutate(Race="caudatum") %>%
  select(-tmp)
kafir <- read.delim("/home/roberto/Sorghum/Evol_model/LD/MAF/kafir", header = F) %>%
  `colnames<-`(c("ID", "tmp")) %>%
  mutate(Race="kafir") %>%
  select(-tmp)
durra <- read.delim("/home/roberto/Sorghum/Evol_model/LD/MAF/durra", header = F) %>%
  `colnames<-`(c("ID", "tmp")) %>%
  mutate(Race="durra") %>%
  select(-tmp)
guinea <- read.delim("/home/roberto/Sorghum/Evol_model/LD/MAF/guinea", header = F) %>%
  `colnames<-`(c("ID", "tmp")) %>%
  mutate(Race="guinea") %>%
  select(-tmp) %>%
  filter(ID != "PI660565")



multi  <- rbind(guinea, caudatum)
id     <- as.character(multi$ID)
pop    <- multi$Race

snpgdsFst(genofile, sample.id=id, population=as.factor(pop), method="W&C84")


```




Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
